A comparison of two second order traffic flow models

### 2015-03-13 FirstDraftMaterials/Draft.tex
Taking out some images

\begin{figure}[H]
 \centering
 \subfigure[$\lambda_1$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the U plane passing through
  the point $(\rho_*, v_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U.jpg}
   }
    \subfigure[$\lambda_1$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the M plane passing through 
 the point $(\rho_*,m_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M.jpg}
   }
       \subfigure[$\lambda_1$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the Y plane passing through 
 the point $(\rho_*, y_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ 
 in each of the different planes. Since the loci and integral curves coincide, they are 
 both simply called the ``curves'' in the captions of the above figures. 
 Figures (c), (f), (i) show both curves for a given point in each plane.}
  \label{fig:AR_curves}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U.jpg}
   }
    \subfigure[Valid waves for the point $q_l$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_ql.jpg}
   }
    \subfigure[Valid waves for the point $q_r$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_qr.jpg}
   }
    \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M.jpg}
   }
 \subfigure[Valid waves for the point $q_l$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_ql.jpg}
   }
 \subfigure[Valid waves for the point $q_r$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_qr.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures showing the calculation of the valid waves for a given point. Figures (a)
  and (d) show the $\lambda_1$ curves in black with the $\lambda_1$ contours 
  in cyan. The other figures show valid shocks in red and valid rarefaction 
  waves in green. The contact discontinuity is shown in blue.}
   \label{fig:AR_validity}
\end{figure}

>>>>

\begin{figure}[H]
 \centering
    \subfigure[$\lambda_1$-curves.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve passing through 
 the point $(\rho_*,m_*)$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$. 
 Since the loci and integral curves coincide, they are 
 both simply called the ``curves'' in the captions of the above figures. 
 Figure (c) shows both curves for a given point.}
  \label{fig:AR_curves}
\end{figure}

@@

\begin{figure}[H]
 \centering
    \subfigure[$\lambda_1$-curves with contours of $\lambda_1$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M.jpg}
   }
 \subfigure[Valid waves for the point $q_l$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_ql.jpg}
   }
 \subfigure[Valid waves for the point $q_r$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_qr.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures showing the calculation of the valid waves for a given point. Figures (a)
  and (d) show the $\lambda_1$ curves in black with the $\lambda_1$ contours 
  in cyan. The other figures show valid shocks in red and valid rarefaction 
  waves in green. The contact discontinuity is shown in blue.}
   \label{fig:AR_validity}
\end{figure}
